---
output: github_document
---

# R6 - with extensions

<!-- badges: start -->
<!-- badges: end -->

Currently R6 supports overrides for the default `print` and `plot` functions in R but leaves out 
basic operation overrides such as addition, subtraction, multiplication, division, etc. This fork
extends the R6 reference class to inclide these.

The override methods must be defined in the `private` section of the class declaration. Currently
the following overrides can be defined:  

* `'+'`
* `'-'`
* `'*'`
* `'/'`
* `'^'`

## Installation

Install this package straight from this repo:

``` r
devtools::install_github("zachzIAM/R6")
```

## Examples
``` r
library(R6)
```

### Addition
This is a basic example which shows you how to solve a common problem:
```{r add}
with_add <- R6::R6Class(
  classname = "with_add",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '+' = function(e2) {
      x = self$x + e2$x
      y = self$y + e2$y
      with_add$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

add <- with_add$new(5, rnorm(1))
result <- add + add
cat(paste0("x = ", result$x, "; y = ", result$y))
```



### Subtraction
``` {r subtract}
with_sub <- R6::R6Class(
  classname = "with_sub",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '-' = function(e2) {
      x = self$x - e2$x
      y = self$y - e2$y
      with_sub$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

sub <- with_sub$new(5, rnorm(1))
result <- sub - sub
cat(paste0("x = ", result$x, "; y = ", result$y))
```

### Multiplication
``` {r multiply}
with_mult <- R6::R6Class(
  classname = "with_mult",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '*' = function(e2) {
      x = self$x * e2$x
      y = self$y * e2$y
      with_mult$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

mult <- with_mult$new(5, rnorm(1))
result <- mult * mult
cat(paste0("x = ", result$x, "; y = ", result$y))
```

### Division
``` {r divide}
with_div <- R6::R6Class(
  classname = "with_div",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '/' = function(e2) {
      x = self$x / e2$x
      y = self$y / e2$y
      with_div$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

div <- with_div$new(5, rnorm(1))
result <- div / div
cat(paste0("x = ", result$x, "; y = ", result$y))
```

### Exponentiation
``` {r exponentiate}
with_pow <- R6::R6Class(
  classname = "with_pow",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '^' = function(e2) {
      x = self$x ^ e2$x
      y = self$y ^ e2$y
      with_pow$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

pow <- with_pow$new(5, rnorm(1))
result <- pow ^ pow
cat(paste0("x = ", result$x, "; y = ", result$y))
```

