---
output: github_document
---

# R6 - with extensions

<!-- badges: start -->
<!-- badges: end -->

## Motivation  
Currently R6 supports overrides for the default `print` and `plot` functions in R but leaves out 
basic operation overrides such as addition, subtraction, multiplication, division, etc. This fork
extends the R6 reference class to inclide these.

The override methods must be defined in the `private` section of the class declaration. Currently
the following overrides can be defined:  

* `'+'`
* `'-'`
* `'*'`
* `'/'`
* `'^'`

## On basic operators and R6
There is probably a good reason R6 have not incorporated basic operators already. E.g. overriding
the `$` and `$<-` operators (if at all possible) would potentially break the whole R6 structure
since it uses that syntax to accessing a given class instance's methods, properties and variables.
The same applies to the `[`, `[<-`, `[[` and `[[<-` basic operators.

On the other hand the basic logical and arithmetic operators are (IMO) fair game. Besides the
overrides described above the following additional operation overrides can potentially be added in
the future:

* `%%`
* `%*%`
* `%/%`
* `<`
* `>`
* `<=`
* `>=`
* `==`
* `!=`
* `|`
* `||`
* `&`
* `&&`
* `!`

## Not covered...
Overrides like this can extend quite far... e.g. if we already have basic operators, plot and print 
overrides then why not allow for other Primitives such as `sum`, `length`, `abs`, etc. This is beyond
the scope of this fork.

## Installation

Install this package straight from this repo:

``` r
devtools::install_github("zachzIAM/R6")
```

## Examples
``` r
library(R6)
```

### Addition
This is a basic example which shows you how to solve a common problem:
```{r echo=FALSE}
set.seed(1)
```

```{r add}
with_add <- R6::R6Class(
  classname = "with_add",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '+' = function(e2) {
      x = self$x + e2$x
      y = self$y + e2$y
      with_add$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

add <- with_add$new(5, rnorm(1))
result <- add + add
cat(paste0("x = ", result$x, "; y = ", result$y))
```



### Subtraction
``` {r subtract}
with_sub <- R6::R6Class(
  classname = "with_sub",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '-' = function(e2) {
      x = self$x - e2$x
      y = self$y - e2$y
      with_sub$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

sub <- with_sub$new(5, rnorm(1))
result <- sub - sub
cat(paste0("x = ", result$x, "; y = ", result$y))
```

### Multiplication
``` {r multiply}
with_mult <- R6::R6Class(
  classname = "with_mult",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '*' = function(e2) {
      x = self$x * e2$x
      y = self$y * e2$y
      with_mult$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

mult <- with_mult$new(5, rnorm(1))
result <- mult * mult
cat(paste0("x = ", result$x, "; y = ", result$y))
```

### Division
``` {r divide}
with_div <- R6::R6Class(
  classname = "with_div",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '/' = function(e2) {
      x = self$x / e2$x
      y = self$y / e2$y
      with_div$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

div <- with_div$new(5, rnorm(1))
result <- div / div
cat(paste0("x = ", result$x, "; y = ", result$y))
```

### Exponentiation
``` {r exponentiate}
with_pow <- R6::R6Class(
  classname = "with_pow",
  public = list(
    x = NULL,
    initialize = function(x, y) {
      self$x = x
      private$.y = y
    }
  ),
  private = list(
    .y = NULL,
    '^' = function(e2) {
      x = self$x ^ e2$x
      y = self$y ^ e2$y
      with_pow$new(x, y)
    }
  ),
  active = list(
    y = function() {
      private$.y
    }
  )
)

pow <- with_pow$new(5, rnorm(1))
result <- pow ^ pow
cat(paste0("x = ", result$x, "; y = ", result$y))
```
